Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-09-05 main_paper.tex
Typo on paragraph on CCF.

CCT show that the bias resulting from undersmoothing can be estimated and they
provide a bias-corrected treatment effect estimator that remains
asymptotically unbiased even when the bandwidth converges to zero at the
AMSE-optimal rate. They also show that this bias-correction term contributes
to the asymptotic variance of the resulting treatment effect estimator and
provide a new formula for the asymptotic variance of the bias-corrected
estimator. The resulting confidence intervals have accurate coverage even when
the naive RD interval does not.
Furthermore, as shown by \citet{CCF15}, these intervals can achieve faster
convergence rates than previously believed, outperforming intervals produced
by undersmoothing in some settings while maintaining grater robustness to
the choice of bandwidth parameter. Previous research by \citet{Hall93} and
\citet{Neumann97} has found that undersmoothing outperforms naive
bias-corrected confidence intervals, but \citet{CCF15} show that the naive
variance estimator implicitly requires more restrictions than CCT's
expression and those restrictions artificially limit the intervals'
performance.

>>>>

CCT show that the bias resulting from undersmoothing can be estimated and they
provide a bias-corrected treatment effect estimator that remains
asymptotically unbiased even when the bandwidth converges to zero at the
AMSE-optimal rate. They also show that this bias-correction term contributes
to the asymptotic variance of the resulting treatment effect estimator and
provide a new formula for the asymptotic variance of the bias-corrected
estimator. The resulting confidence intervals have accurate coverage even when
the naive RD interval does not.
Furthermore, as shown by \citet{CCF15}, these intervals can achieve faster
convergence rates than previously believed, outperforming intervals produced
by undersmoothing in some settings while maintaining greater robustness to
the choice of bandwidth parameter. Previous research by \citet{Hall93} and
\citet{Neumann97} has found that undersmoothing outperforms naive
bias-corrected confidence intervals, but \citet{CCF15} show that the naive
variance estimator implicitly requires more restrictions than CCT's
expression and those restrictions artificially limit the intervals'
performance.
